Learning can mediate the evolution of\\ (cheap and costly) signals of quality

### 2020-11-25 Presentations/GenesAsEnviron.tex
AccFunc: use countour3 in evolDist to include several panels in a figure. Figure files: use several files to upload one scenario. Aga_figures: finished Improve cluster analysis cue_compt.cpp: Allow to insert types at the beggining of the simulations New simulation with different sd for the mutation kernel

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones PhD.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor}

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
November 02, 2020}

@@

@@

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \includegraphics[width=0.4\linewidth]{../Images/begging} \includegraphics[width=0.4\linewidth]{../Images/broodparasite} \includegraphics[width=0.4\linewidth]{../Images/dominance} \end{center}

@@

\begin{center}\includegraphics[height=0.8\textheight]{../Images//hosp_alexandra_mackenzie} \end{center}

@@

\begin{frame}{The handicap principle}
\protect\hypertarget{the-handicap-principle-1}{}

\begin{block}{Badges of status}

\begin{center}\includegraphics[width=0.9\linewidth]{../Images//comSystemBot} \end{center}

(Botero et al. 2010)

\begin{frame}{Are bibs really badges?}
\protect\hypertarget{are-bibs-really-badges}{}

\begin{flushleft}\includegraphics[width=0.3\linewidth]{../Images/Sanchez-Tojar_2018} \end{flushleft}

@@

\vspace{-0.5cm}

\begin{block}{Comunication}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-19-1} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-20-1} \end{center}

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-21-1} \end{center}

@@

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/alphaAct_/alphaAct0.6learnDyn} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}

@@

\begin{frame}{Badges of Status: do they matter?}
\protect\hypertarget{badges-of-status-do-they-matter}{}

\begin{block}{Behavioural interactions}

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol1_/compClustRep_betCost5} \end{center}

--\textgreater{} --\textgreater{} --\textgreater{}

\begin{frame}{The evolution of cheap Badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol4_/evolDyn13_nIntGroup2000} \end{center}

\begin{frame}{The evolution of cheap Badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status-1}{}

\begin{figure}

\includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol4_/evolDistAlpha13_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol4_/evolDistBeta13_nIntGroup2000} \includegraphics[height=0.28\textheight]{../Simulations/nIntGroupEvol4_/evolDistBadge13_nIntGroup2000} \hfill{}

\caption{alpha - beta -Badge}\label{fig:unnamed-chunk-27}
\end{figure}

\begin{frame}{The evolution of cheap Badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status-2}{}

\begin{block}{How often does it happen?}

\begin{flushleft}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol1_/corrAlphBet_nIntGroup2000} \end{flushleft}

\begin{frame}{The evolution of cheap Badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status-3}{}

\begin{block}{Does it matter?}

\small

Behavioural interactions splitting up the replicates according to the
number of ``types'' that evolve

\begin{flushleft}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupEvol1_/BehavIntAllClusters_nIntGroup2000} \end{flushleft}

--\textgreater{}

--\textgreater{}

@@

\tiny

Here, I vary the aggressive tendency for unlearned individuals in these
three set ups.

Agressive, peaceful, clever (starts at the ESS of the classic hawk-dove
game)

\begin{flushleft}\includegraphics[width=0.9\linewidth]{../Images/cartoonRBF_InitAct} \end{flushleft}

@@

\begin{block}{The peaceful}

Variation among replicates

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDynALL_initAct2} \end{flushleft}

@@

\begin{block}{The peaceful}

Variation within one replicate

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDyn2_initAct2} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-3}{}

\begin{block}{The peaceful}

Changes in the frequency distributions

\begin{flushleft}\includegraphics[height=0.28\textheight]{../Simulations/initAct_/evolDistAlpha2_initAct2} \includegraphics[height=0.28\textheight]{../Simulations/initAct_/evolDistBeta2_initAct2} \includegraphics[height=0.28\textheight]{../Simulations/initAct_/evolDistBadge2_initAct2} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-4}{}

\begin{block}{The peaceful}

Favours variation and cheap signals

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/corrAlphBet_initAct2} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-5}{}

\begin{block}{The aggressive}

Variation among replicates

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDynALL_initAct-2} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-6}{}

\begin{block}{The aggressive}

Variation within one replicate

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDyn0_initAct-2} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-7}{}

\begin{block}{The aggressive}

Disfavours variation and signal evolution - no signalling

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/corrAlphBet_initAct-2} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-8}{}

\begin{block}{The clever (ESS)}

Variation among replicates

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDynALL_initAct-0.69} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-9}{}

\begin{block}{The clever (ESS)}

Variation within one replicate

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/evolDyn0_initAct-0.69} \end{flushleft}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-10}{}

\begin{block}{The clever (ESS)}

Signal evolution seems to be driven by drift. Most replicates end up in
one of the two extremes

\begin{flushleft}\includegraphics[width=1\linewidth]{../Simulations/initAct_/corrAlphBet_initAct-0.69} \end{flushleft}

@@

\begin{itemize}
\tightlist
\item
  Learning can mediate costly signals
\item
  More expensive signals seem be more likely to evolve
\item
  Less expensive signals provide more information
\item
  Local interactions do not impede the evolution of costly signals (as
  has been suggested)
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Learning mediates the evolution of polymorphisms with ``honest'' and
  ``dishonest'' individuals
\item
  Under local interactions learning seems to allow the evolution of IR
\item
  Cheap signals depend on the innate level of aggression (before
  learning) of individuals
\item
  Peace begets heterogeneity, aggression begets homogeneity
\end{itemize}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-botero_Evolution_2010}{}%
Botero, C. A, I. Pen, J. Komdeur, and F. J Weissing. 2010. ``The
Evolution of Individual Variation in Communication Strategies.''
\emph{Evolution} 64 (11): 3123--33.

\leavevmode\hypertarget{ref-grafen_Biological_1990}{}%
Grafen, Alan. 1990. ``Biological Signals as Handicaps.'' \emph{Journal
of Theoretical Biology} 144 (4): 517--46.
\url{https://doi.org/10.1016/S0022-5193(05)80088-8}.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones PhD.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{longtable,booktabs}
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor}

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
November 17 - 2020}

@@

\begin{frame}{Acknowledgements}
\protect\hypertarget{acknowledgements}{}

\begin{longtable}[]{@{}ccc@{}}
\toprule
\includegraphics[width=0.33\textwidth,height=\textheight]{../Images/redouan.jpg}
&
\includegraphics[width=0.23\textwidth,height=\textheight]{../Images/olof-leimar.png}
&
\includegraphics[width=0.32\textwidth,height=\textheight]{../Images/danielcadena.jpg}\tabularnewline
\midrule
\endhead
\emph{R. Bshary} & \emph{O. Leimar} & \emph{D. Cadena}\tabularnewline
\bottomrule
\end{longtable}

\includegraphics[width=0.35\textwidth,height=\textheight]{../Images/UNINE_cmjn.jpg}
\includegraphics[width=0.45\textwidth,height=\textheight]{../Images/logo_largo.png}

@@

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \end{center}

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/dominance} \end{center}

@@

\begin{center}\includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_strong} \includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_weak} \end{center}

@@

@@

\vspace{-0.3cm}

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-17-1} \end{center}

\begin{block}{Communication}

@@

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-18-1} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-19-1} \end{center}

@@

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn} \end{center}

@@

@@

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}

@@

\begin{center}\includegraphics[height=0.9\textheight]{../Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}

@@

\begin{frame}{The evolution of cheap badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000} \end{center}

@@

\includegraphics[width=0.45\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn}
\includegraphics[width=0.45\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-24-2}

@@

\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_1}

@@

\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_}

@@

\begin{itemize}
\tightlist
\item
  Learning can mediate costly signals
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  Learning mediates the evolution of polymorphisms with ``honest'' and
  ``dishonest'' individuals
\item
  Cheap signals depend on the innate level of aggression (before
  learning) of individuals
\end{itemize}

@@

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-grafen_Biological_1990}{}%
Grafen, Alan. 1990. ``Biological Signals as Handicaps.'' \emph{Journal
of Theoretical Biology} 144 (4): 517--46.
\url{https://doi.org/10.1016/S0022-5193(05)80088-8}.
